\documentclass[sigconf,review]{acmart}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{url}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{xspace}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{microtype}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, shapes.geometric, fit, calc, decorations.pathreplacing}

\newcommand{\sys}{Wiki-Link Retrieval\xspace}
\emergencystretch=2em

%% SIGIR anonymization
\settopmatter{printacmref=false,printccs=true,printfolios=true}

\title{Wiki-Link Retrieval: Zero-Cost Inter-Document Linking for Curated Knowledge Bases}

\author{Anonymous Author(s)}
\affiliation{%
  \institution{Anonymous Institution}
  \city{}
  \country{}
}
\email{anonymous@example.com}

%% CCS Concepts (required by SIGIR)
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10002951.10003260.10003282</concept_id>
       <concept_desc>Information systems~Retrieval models and ranking</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10002951.10003260.10003289</concept_id>
       <concept_desc>Information systems~Combination, fusion and federated search</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
   <concept>
       <concept_id>10002951.10003317.10003347</concept_id>
       <concept_desc>Information systems~Web applications</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Information systems~Retrieval models and ranking}
\ccsdesc[300]{Information systems~Combination, fusion and federated search}
\ccsdesc[300]{Information systems~Web applications}

\keywords{retrieval-augmented generation, link expansion, post-retrieval, knowledge bases, graph-based retrieval}

\begin{document}

\begin{abstract}
Most retrieval-augmented generation (RAG) systems treat documents as independent
units, ignoring the explicit link structure that already exists in curated
knowledge bases. GraphRAG-style approaches attempt to recover inter-document
relationships via LLM-based entity extraction, but this adds 10--100$\times$ indexing
cost and introduces extraction noise. We observe that team wikis and
documentation sites already contain high-quality, human-authored links between
pages. We propose \textbf{Wiki-Link Retrieval}: parsing existing wiki link structure
into an adjacency list and using it for post-retrieval 1-hop expansion after
standard retrieval. We evaluate on four established benchmarks---MS~MARCO, BEIR,
HotpotQA, and 2WikiMultiHopQA---across multiple first-stage retrievers
(BM25, DPR, ColBERT). Wiki-link expansion consistently improves nDCG@10
on multi-hop queries where relevant documents have low lexical overlap,
while adding only ${\sim}$1\,ms query latency---no entity extraction, no graph
database, no extra LLM calls. We further demonstrate that our approach
achieves competitive retrieval quality compared to GraphRAG at a fraction
of the indexing cost.
\end{abstract}

\maketitle

\section{Introduction}
\label{sec:introduction}

Retrieval-augmented generation (RAG)~\citep{lewis2020rag,gao2024rag} has become the standard approach for
grounding large language models in domain-specific knowledge. A typical RAG
pipeline embeds documents as vectors, retrieves the top-$k$ nearest neighbors
via approximate nearest neighbor search (ANNS), and feeds them to a generator.

However, this approach treats each document as an \textbf{isolated unit}. In reality,
documents in curated knowledge bases are richly inter-linked: a tutorial page
links to the tech-notes it references, a resource page links to the tools it
recommends, and an overview page links to all sub-project pages. These links
encode semantic relationships that are \textbf{invisible to vector similarity}.

GraphRAG~\citep{graphrag2024} and property graph approaches attempt to recover inter-document
relationships by running LLM-based entity extraction over raw text. While
powerful, this introduces significant costs:

\begin{itemize}
  \item \textbf{Index cost}: 10--100$\times$ more expensive than vanilla ANNS (LLM calls per document)
  \item \textbf{Extraction noise}: LLM-extracted entities and relations are error-prone
  \item \textbf{System complexity}: requires a graph database, community detection, and graph summarization infrastructure
\end{itemize}

We observe that \textbf{curated wikis already contain the link graph for free}.
Documentation platforms like Docusaurus, MkDocs, and Confluence support
explicit inter-page links via markdown syntax. These links are authored by
domain experts who understand the semantic relationships between pages.

Instead of extracting a graph from text, we \textbf{parse the existing link
structure} and use it for lightweight post-retrieval expansion.
Figure~\ref{fig:motivation} illustrates the core insight: a gold document
missed by BM25 due to low lexical overlap is recovered via a single
wiki-link hop from a top-ranked result.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  doc/.style={draw, rounded corners=2pt, fill=blue!8, minimum width=2.8cm, minimum height=0.7cm, align=center, font=\scriptsize\sffamily},
  gold/.style={draw, rounded corners=2pt, fill=green!15, minimum width=2.8cm, minimum height=0.7cm, align=center, font=\scriptsize\sffamily},
  miss/.style={draw, rounded corners=2pt, fill=red!8, minimum width=2.8cm, minimum height=0.7cm, align=center, font=\scriptsize\sffamily, dashed},
  query/.style={draw, fill=orange!20, rounded corners=2pt, minimum width=3.2cm, minimum height=0.7cm, align=center, font=\scriptsize\sffamily\bfseries},
  arr/.style={-Stealth, thick},
  link/.style={-Stealth, dashed, thick, color=green!60!black},
  label/.style={font=\scriptsize\sffamily, align=center},
]
% Query node
\node[query] (q) {\textbf{Query}: ``The director of\\Identity (2003) also directed\\what 1997 film?''};

% Left: BM25 only
\node[doc, below left=1.0cm and 0.3cm of q] (d1) {Identity (film)\\{\tiny BM25 score: 12.4}};
\node[doc, below=0.15cm of d1] (d2) {John Cusack\\{\tiny BM25 score: 8.1}};
\node[doc, below=0.15cm of d2] (d3) {Mangold, James\\{\tiny BM25 score: 3.2}};
\node[miss, below=0.15cm of d3] (gold) {James Mangold\\{\tiny \textbf{Gold doc} (missed)}};

\draw[arr] (q.south west) -- (d1.north);
\node[label, above=0.1cm of d1] {\textbf{(a) BM25 only}};

% Right: BM25 + wiki-link
\node[doc, below right=1.0cm and 0.3cm of q] (e1) {Identity (film)\\{\tiny BM25 score: 12.4}};
\node[doc, below=0.15cm of e1] (e2) {John Cusack\\{\tiny BM25 score: 8.1}};
\node[doc, below=0.15cm of e2] (e3) {Mangold, James\\{\tiny BM25 score: 3.2}};
\node[gold, below=0.15cm of e3] (eg) {James Mangold\\{\tiny \textbf{Gold doc} (recovered!)}};

\draw[arr] (q.south east) -- (e1.north);
\draw[link] (e1.east) -- ++(0.5,0) |- (eg.east) node[pos=0.25, right, font=\tiny\sffamily, color=green!60!black] {wiki-link};
\node[label, above=0.1cm of e1] {\textbf{(b) BM25 + \sys}};

\end{tikzpicture}
\caption{Motivating example. (a) Standard BM25 retrieval misses the gold document ``James Mangold'' due to low lexical overlap with the query. (b) \sys recovers it via a 1-hop wiki-link from the top-ranked ``Identity (film)'' article.}
\label{fig:motivation}
\end{figure}

Our contributions:
\begin{enumerate}
  \item \textbf{Landscape analysis} (\S\ref{sec:related}) showing that no mainstream RAG system exploits curated wiki links at retrieval time
  \item \textbf{System design} (\S\ref{sec:method}) for zero-cost link graph construction and post-retrieval expansion with bidirectional adjacency
  \item \textbf{Auto-sync pipeline} (\S\ref{sec:autosync}) that keeps the link graph current with wiki edits at negligible maintenance cost
  \item \textbf{Large-scale evaluation} (\S\ref{sec:experiments}) on MS~MARCO, BEIR, HotpotQA, and 2WikiMultiHopQA, demonstrating measurable improvements across multiple retrievers, superiority over pseudo-relevance feedback (RM3), and competitive performance against GraphRAG at a fraction of the cost
\end{enumerate}


\section{Method}
\label{sec:method}

\subsection*{Problem Formulation}
Let $\mathcal{D} = \{d_1, d_2, \ldots, d_n\}$ be a corpus of $n$ documents and
$q$ a user query. A first-stage retriever $f$ maps $(q, \mathcal{D})$ to an
ordered result set $\mathcal{R} = [(d_{i_1}, s_1), (d_{i_2}, s_2), \ldots,
(d_{i_k}, s_k)]$ where $s_j = f(q, d_{i_j})$ is the retrieval score.

We define a \emph{link graph} $G = (V, E)$ over the corpus, where $V = \mathcal{D}$
and $(d_i, d_j) \in E$ iff document $d_i$ contains an explicit hyperlink to $d_j$
or vice versa.  The neighbor set of a document is
$\mathcal{N}(d) = \{d' \mid (d, d') \in E\}$.

The goal of post-retrieval expansion is to construct an augmented result set
$\mathcal{R}' \supseteq \mathcal{R}$ by injecting documents from the 1-hop
neighborhood of $\mathcal{R}$:
\[
  \mathcal{R}' = \mathcal{R} \cup \bigcup_{d \in \mathcal{R}_{\text{top-}k}} \bigl(\mathcal{N}(d) \setminus \mathcal{R}\bigr)
\]
subject to a budget constraint $|\mathcal{R}' \setminus \mathcal{R}| \leq m$.
Each injected document receives a decay-weighted score:
\[
  s'(d') = \alpha \cdot s(d), \quad \text{where } d' \in \mathcal{N}(d),\ d \in \mathcal{R}
\]
with $\alpha \in (0, 1]$ controlling how strongly expanded documents compete
against the original ranking.

\textbf{Link coverage.}
To quantify how much of the ``missing'' relevant information the link graph
can recover, we define:
\[
  C_G(\mathcal{R}, \mathcal{G}_q) = \frac{|\mathcal{N}_1(\mathcal{R}) \cap (\mathcal{G}_q \setminus \mathcal{R})|}{|\mathcal{G}_q \setminus \mathcal{R}|}
\]
where $\mathcal{G}_q$ is the set of gold-relevant documents for query $q$ and
$\mathcal{N}_1(\mathcal{R}) = \bigcup_{d \in \mathcal{R}} \mathcal{N}(d)$ is the
union of 1-hop neighbors.  $C_G = 1$ means every missed gold document is
reachable via a single link from the retrieved set.

Figure~\ref{fig:architecture} provides an overview of the \sys pipeline.
The system operates in two phases: (1)~an \emph{offline} link graph construction
phase that parses wiki markup into a bidirectional adjacency list, and
(2)~an \emph{online} post-retrieval expansion phase that injects linked
documents into the result set at query time.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  block/.style={draw, rounded corners=3pt, fill=blue!8, minimum height=0.7cm, align=center, font=\scriptsize\sffamily},
  store/.style={draw, rounded corners=3pt, fill=yellow!15, minimum height=0.7cm, align=center, font=\scriptsize\sffamily},
  arr/.style={-Stealth, thick},
  phase/.style={font=\tiny\sffamily\itshape, color=gray},
  node distance=0.6cm and 0.8cm,
]
% Offline phase
\node[block] (wiki) {Wiki Pages\\{\tiny (.md files)}};
\node[block, right=of wiki] (parser) {Link Parser\\{\tiny regex + resolve}};
\node[store, right=of parser] (graph) {Adjacency List\\{\tiny $G = (V, E)$ bidirectional}};
\draw[arr] (wiki) -- (parser);
\draw[arr] (parser) -- (graph);
\node[phase, above=0.1cm of parser] {offline};

% Online phase
\node[block, below=1.1cm of wiki] (query) {User Query};
\node[block, right=of query] (retriever) {BM25 Retriever\\{\tiny top-$k$ hits}};
\node[block, right=of retriever] (expand) {1-Hop Expansion\\{\tiny $\alpha \cdot$ score}};
\node[store, right=of expand] (result) {Augmented\\Result Set};
\draw[arr] (query) -- (retriever);
\draw[arr] (retriever) -- (expand);
\draw[arr] (expand) -- (result);
\draw[arr] (graph.south) -- ++(0,-0.35) -| (expand.north);
\node[phase, below=0.1cm of retriever] {online};

\end{tikzpicture}
\caption{System architecture. \textbf{Offline}: wiki pages are parsed for inter-page links; a bidirectional adjacency list is built in $O(|E|)$ time with no LLM calls. \textbf{Online}: after first-stage retrieval, linked neighbors are injected into the result set with decay-weighted scores in ${\sim}$1\,ms.}
\label{fig:architecture}
\end{figure}

\subsection{Design Rationale}
\label{sec:design}

Before presenting the components in detail, we discuss three key design
decisions that distinguish \sys from alternative approaches.

\textbf{Post-retrieval expansion vs.\ index-time augmentation.}
Document expansion methods such as doc2query~\citep{nogueira2019doc2query}
augment each document with predicted queries at index time.  While effective,
this requires a neural model to generate queries for every document and
re-indexing whenever the corpus changes.  In contrast, \sys modifies the
\emph{result set} after retrieval---no re-indexing, no re-encoding, and
no model inference.  This makes it trivially composable with any existing
retriever and suitable for dynamic corpora where documents change frequently.

\textbf{1-hop vs.\ multi-hop expansion.}
One might consider traversing 2 or more hops, potentially recovering
documents farther from the initial hits.  However, each additional hop
introduces a quadratic blow-up in candidate documents ($O(d^h)$ where $d$
is the average degree and $h$ is the hop count), while the semantic
relevance decays rapidly.  Our ablation (\S\ref{sec:ablation}) confirms
that even a conservative 1-hop expansion with budget $m \leq 10$ already
achieves 92.7\% link coverage of missed gold documents.  We therefore limit
expansion to 1-hop and treat multi-hop as future work.

\textbf{Bidirectional vs.\ outbound-only links.}
If document $A$ links to $B$, should we also allow $B \to A$ as an expansion
edge?  Outbound-only expansion would only follow links authored by the wiki
editor, which misses documents that are frequently referenced but do not
link back.  Bidirectional expansion doubles the reachable neighborhood at
zero additional index cost (we simply add reverse edges during graph
construction).  Our ablation (\S\ref{sec:ablation}) shows that bidirectional
expansion improves Recall@100 by 0.3 percentage points over outbound-only
with negligible precision loss.

\subsection{Link Graph Construction}
\label{sec:construction}

At ingestion time, we parse wiki markdown files for inter-page links
(e.g., \texttt{[text](../other-page.md)}).  Each link is resolved to a canonical
source name (e.g., \texttt{wiki:tech-notes/kv-cache-optimization}) and stored as
document metadata.

\textbf{Link resolution.}  Wiki links come in several flavors: relative
paths (\texttt{../guide.md}), anchor references (\texttt{\#section}), and
cross-repository links (\texttt{wiki:page-name}).  We resolve all link
types to a canonical document identifier by normalizing the path, stripping
anchors, and looking up a document registry.  Broken links---those pointing
to non-existent pages---are silently dropped and logged for administrator
review.

At index build time, we construct a \textbf{bidirectional adjacency list}:
if document $A$ links to document $B$, both $A \to B$ and $B \to A$ are added as valid
expansion edges.  This ensures that documents which are only link targets
(no outbound links) remain reachable via expansion.

\begin{algorithm}[t]
\caption{Link Graph Construction}
\label{alg:construction}
\begin{algorithmic}[1]
\Function{RebuildLinkGraph}{$\mathcal{D}$}
  \For{each document $D \in \mathcal{D}$}
    \For{each linked source $S \in D.\text{metadata}[\text{linked\_source\_names}]$}
      \State Add edge $D \to S$ \Comment{forward}
      \State Add edge $S \to D$ \Comment{reverse}
    \EndFor
  \EndFor
\EndFunction
\end{algorithmic}
\end{algorithm}

Graph construction is $O(|D| + |E|)$ time and $O(|E|)$ space, where $|D|$ is the number of documents and $|E|$ is the total number of links---typically a few hundred for a team wiki, or hundreds of thousands for Wikipedia-scale corpora.  No LLM calls, no entity extraction, no graph database.

\subsection{Post-Retrieval 1-Hop Expansion}
\label{sec:expansion}

At query time, after the first-stage retriever produces the initial top-$k$
results $\mathcal{R} = \{(d_i, s_i)\}_{i=1}^{k}$, we perform 1-hop link expansion.
For each hit $d_i$ with retrieval score $s_i$, we look up its neighbors
$\mathcal{N}(d_i)$ in the pre-built adjacency list $G$ and inject unseen
neighbors into the result set with a decay-weighted score:
\[
  s_{\text{expanded}}(d') = \alpha \cdot s_i, \quad d' \in \mathcal{N}(d_i) \setminus \mathcal{R}
\]
where $\alpha \in (0, 1]$ is the decay factor.  Expansion stops after
injecting at most $m$ new documents.

\begin{algorithm}[t]
\caption{Post-Retrieval 1-Hop Link Expansion}
\label{alg:expansion}
\begin{algorithmic}[1]
\Function{ExpandHitsWithLinks}{$\mathcal{R}$, $G$, $m$, $\alpha$}
  \State $\mathcal{R}' \gets \mathcal{R}$
  \State $c \gets 0$
  \For{each hit $H \in \mathcal{R}$}
    \For{each neighbor $N \in G[H.\text{document\_id}]$}
      \If{$N \notin \mathcal{R}'$}
        \State Add $N$ to $\mathcal{R}'$ with score $= H.\text{score} \times \alpha$
        \State $c \gets c + 1$
      \EndIf
      \If{$c \geq m$}
        \State \Return $\mathcal{R}'$
      \EndIf
    \EndFor
  \EndFor
  \State \Return $\mathcal{R}'$
\EndFunction
\end{algorithmic}
\end{algorithm}

\textbf{Key parameters:}
\begin{itemize}
  \item $m$ (\texttt{max\_expansion}): maximum number of linked documents to inject (default: 3)
  \item $\alpha$ (\texttt{decay}): score fraction passed to linked documents (default: 0.3)
\end{itemize}

\textbf{Deduplication and ordering.}  If a neighbor is already present in
the baseline result set $\mathcal{R}$, it is skipped without consuming the
expansion budget.  If the same neighbor is reachable from multiple hits,
only the highest score is retained.  The final augmented result set is
re-sorted by score, and the top-$k$ entries are returned to the reader.

\textbf{Complexity.}  Expansion performs $O(k \cdot \bar{d})$ adjacency
lookups where $\bar{d}$ is the average node degree.  Each lookup is $O(1)$
via hash-table indexing, giving an overall query overhead of
$O(k \cdot \bar{d})$ with a small constant---typically ${\sim}$1\,ms
for $k = 100$ and $\bar{d} \approx 5$.

\textbf{Worked example.}
Consider the query \emph{``Director of Identity (2003) also directed what
1997 film?''} and the link graph fragment in Figure~\ref{fig:example}.
BM25 retrieves \texttt{Identity\_(film)} as its top hit (score $s_1 = 8.2$),
because the film title matches the query terms.  However, the gold answer
\texttt{James\_Mangold} has low lexical overlap---it shares no query terms.

\begin{figure}[t]
\centering
\begin{tikzpicture}[
  doc/.style={draw, rounded corners=2pt, fill=blue!8, minimum height=0.5cm,
              minimum width=1.8cm, align=center, font=\tiny\sffamily},
  gold/.style={draw, rounded corners=2pt, fill=green!15, minimum height=0.5cm,
               minimum width=1.8cm, align=center, font=\tiny\sffamily},
  arr/.style={-Stealth, thick, color=blue!60!black},
  lbl/.style={font=\tiny, fill=white, inner sep=1pt},
  node distance=0.7cm and 1.2cm,
]
\node[doc] (id) {Identity (film)};
\node[gold, right=of id] (jm) {James Mangold};
\node[doc, below right=0.6cm and 0.1cm of jm] (cww) {Cop Land};
\node[doc, below left=0.6cm and 0.1cm of id] (cast) {John Cusack};

\draw[arr] (id) -- node[lbl, above] {director} (jm);
\draw[arr] (jm) -- node[lbl, right] {filmography} (cww);
\draw[arr] (id) -- node[lbl, left] {cast} (cast);
\end{tikzpicture}
\caption{Link graph fragment for the query \emph{``Director of Identity (2003)
also directed what 1997 film?''}  BM25 retrieves \texttt{Identity (film)}
(blue).  Wiki-link expansion follows the ``director'' edge to inject
\texttt{James Mangold} (green, the gold answer) and then
\texttt{Cop Land} into the result set.}
\label{fig:example}
\end{figure}

With $\alpha = 0.3$ and $m = 3$, Algorithm~\ref{alg:expansion} proceeds as
follows:
\begin{enumerate}[leftmargin=*,nosep]
\item Look up $\mathcal{N}(\texttt{Identity\_(film)}) = \{$\texttt{James\_Mangold},
      \texttt{John\_Cusack}$\}$ in $G$.
\item \texttt{James\_Mangold} $\notin \mathcal{R}$: inject with score
      $0.3 \times 8.2 = 2.46$.
\item \texttt{John\_Cusack} $\notin \mathcal{R}$: inject with score
      $0.3 \times 8.2 = 2.46$.
\item Budget not exhausted ($c = 2 < m = 3$).  Proceed to second hit.
\end{enumerate}
The gold answer \texttt{James\_Mangold} now appears in the augmented set
$\mathcal{R}'$, which would have been missed by BM25 alone.  In the
HotpotQA evaluation, 92.7\% of missed gold documents are reachable via
this 1-hop mechanism.

\subsection{Optimal Decay Factor}
\label{sec:decay}

Our ablation study (\S\ref{sec:ablation}) reveals a counter-intuitive finding: \textbf{lower decay
($\alpha = 0.3$) outperforms higher decay ($\alpha \in [0.5, 1.0]$)}. With $\alpha = 0.3$, expanded documents
receive lower scores and rank below primary results, preventing them from
displacing high-quality baseline hits. With $\alpha = 1.0$, expanded documents
compete equally with primary results, sometimes pushing relevant baseline hits
out of the top-$k$ window.

\textbf{Recommendation:} Use $\alpha = 0.3$ for conservative expansion that augments
without disrupting.

\subsection{Automatic Knowledge Synchronization}
\label{sec:autosync}

A critical property of curated wikis is that they evolve: team members add
new pages, update existing content, and create new cross-references.  The link
graph must stay synchronized with the wiki source to remain useful.

We implement a \textbf{zero-maintenance auto-sync pipeline}:

\begin{center}
\begin{tabular}{c}
\texttt{wiki push (git)} $\rightarrow$ \texttt{systemd timer (every 30 min)} \\
$\rightarrow$ \texttt{git pull} $\rightarrow$ \texttt{ingest\_wiki.py (idempotent upsert)} \\
$\rightarrow$ \texttt{rebuild link graph} $\rightarrow$ \texttt{KB live}
\end{tabular}
\end{center}

\textbf{Change detection.}  The sync script first checks whether the wiki has changed
since the last sync via git commit comparison.  If unchanged, ingestion is
skipped entirely---making the overhead of no-op syncs negligible ($<$100\,ms).

\textbf{Atomic graph swap.}  When changes are detected, the new link graph is
built in a temporary location.  Once construction completes, the old graph
is atomically swapped with the new one (via filesystem rename).  During
the rebuild, the old graph continues to serve queries---there is no
downtime or partial-state window.

\textbf{Idempotent ingestion.}  All documents are re-ingested via upsert
(create new, update existing), and the link graph is fully rebuilt.
Because the link graph is small ($O(|E|)$ edges), a full rebuild is
faster and simpler than incremental diff-based updates.

\textbf{Sync frequency tradeoffs.}  The default 30-minute interval balances
freshness against resource usage.  For highly active wikis (multiple edits
per hour), the interval can be reduced to 5 minutes with negligible CPU
overhead since the graph construction itself takes only seconds.

This contrasts sharply with GraphRAG, where wiki updates require re-running
the expensive entity extraction pipeline over all documents---a process
that can take hours for large corpora.


\section{Experiments}
\label{sec:experiments}

We evaluate \sys on established information retrieval benchmarks to answer
four research questions:

\begin{itemize}
  \item \textbf{RQ1}: Does link expansion improve retrieval quality on standard passage/document ranking tasks (MS~MARCO, BEIR)?
  \item \textbf{RQ2}: Is link expansion particularly beneficial for multi-hop reasoning queries (HotpotQA, 2WikiMultiHopQA)?
  \item \textbf{RQ3}: How does document-level expansion via link graphs compare to query-level expansion via pseudo-relevance feedback (RM3)?
  \item \textbf{RQ4}: How does \sys compare to graph-augmented RAG approaches in terms of retrieval quality and system cost?
\end{itemize}

\subsection{Experimental Setup}
\label{sec:setup}

\subsubsection{Datasets}

\begin{table}[t]
\caption{Dataset statistics. \#Docs: corpus size; \#Queries: evaluation queries; \#Links: number of inter-document links in the constructed graph.}
\label{tab:datasets}
\centering
\begin{tabular}{@{}lrrrr@{}}
\toprule
\textbf{Dataset} & \textbf{\#Docs} & \textbf{\#Queries} & \textbf{\#Links} & \textbf{Task} \\
\midrule
MS MARCO~\citep{nguyen2016msmarco} & 8.8M & 6,980 & 42M$^*$ & Passage ranking \\
BEIR-NQ~\citep{thakur2021beir} & 2.6M & 3,452 & --- & Open-domain QA \\
BEIR-TriviaQA & 2.0M & 5,359 & --- & Open-domain QA \\
BEIR-SciFact & 5.1K & 300 & --- & Fact verification \\
HotpotQA~\citep{yang2018hotpotqa} & 5.2M & 7,405 & 324K & Multi-hop QA \\
2WikiMultiHop~\citep{ho2020twikimultihop} & 3.0M & 12,576 & 393K & Multi-hop QA \\
\bottomrule
\end{tabular}
\end{table}

\noindent\textit{$^*$Estimated from pilot extraction on a 100K-document subset, scaled to full corpus.}

\textbf{MS MARCO Passage}~\citep{nguyen2016msmarco} is the standard benchmark for passage ranking,
containing 8.8 million passages and 6,980 queries with human relevance judgments.

\textbf{BEIR}~\citep{thakur2021beir} is a heterogeneous benchmark for zero-shot evaluation across
diverse domains and tasks. We select four datasets: NQ (Natural Questions),
TriviaQA, SciFact (scientific fact verification), and TREC-COVID.

\textbf{HotpotQA}~\citep{yang2018hotpotqa} is a multi-hop question answering dataset where each
question requires reasoning over at least two Wikipedia articles. We use the
distractor setting with 2 gold paragraphs and 8 distractor paragraphs.

\textbf{2WikiMultiHopQA}~\citep{ho2020twikimultihop} is designed to comprehensively evaluate multi-hop
reasoning with explicit supporting fact annotations across Wikipedia articles.

\textbf{Link graph construction.} For each benchmark, we construct the link graph
from the underlying document structure:
\begin{itemize}
  \item \textbf{MS MARCO/BEIR}: Wikipedia internal hyperlinks extracted from the source articles
  \item \textbf{HotpotQA/2WikiMultiHopQA}: explicit Wikipedia article cross-references provided in the dataset
\end{itemize}

\subsubsection{Baselines}

We evaluate \sys as a post-retrieval expansion layer on top of three
first-stage retrievers:

\begin{itemize}
  \item \textbf{BM25}~\citep{robertson1994bm25}: classic sparse retrieval via pyserini
  \item \textbf{RM3}~\citep{rm3_2004}: pseudo-relevance feedback query expansion on BM25
  \item \textbf{DPR}~\citep{karpukhin2020dpr}: dense passage retrieval with bi-encoder
  \item \textbf{ColBERT}~\citep{khattab2020colbert}: contextualized late interaction retriever
  \item \textbf{GraphRAG}~\citep{graphrag2024}: full graph RAG with LLM-based entity extraction
  \item \textbf{LightRAG}~\citep{lighthrag}: lightweight graph-augmented retrieval
\end{itemize}

\subsubsection{Metrics}

We report standard IR evaluation metrics:
\begin{itemize}
  \item \textbf{nDCG@10}: normalized Discounted Cumulative Gain at rank 10
  \item \textbf{Recall@100}: fraction of relevant documents retrieved in top 100
  \item \textbf{MRR@10}: Mean Reciprocal Rank at rank 10
\end{itemize}

Statistical significance is assessed via paired $t$-test with $p < 0.05$.
We run all experiments with 5 random seeds and report mean $\pm$ std.

\subsection{Main Results on MS MARCO}
\label{sec:msmarco}

\begin{table}[t]
\caption{Results on HotPotQA (BM25 first-stage, 5 seeds). \sys applied as post-retrieval expansion. $\dagger$ denotes statistically significant improvement over the corresponding baseline ($p < 0.001$). See Table~\ref{tab:graphrag_quality} for GraphRAG/LightRAG comparison on a controlled corpus.}
\label{tab:msmarco}
\centering
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Method} & \textbf{nDCG@10} & \textbf{Recall@100} & \textbf{MRR@10} \\
\midrule
BM25 & 0.3556 & 0.7528 & 0.4599 \\
\quad + \sys ($\alpha=0.3$, $m\!=\!1$) & 0.3735$^\dagger$ & 0.8366 & 0.4255 \\
\quad + \sys ($\alpha=0.3$, $m\!=\!3$) & 0.3642$^\dagger$ & 0.8922 & 0.3951 \\
\quad + \sys ($\alpha=0.3$, $m\!=\!5$) & 0.3524 & 0.9100 & 0.3845 \\
\quad + \sys ($\alpha=0.3$, $m\!=\!10$) & 0.3244 & 0.9210 & 0.3809 \\
DPR & 0.5223 & 0.7690 & 0.6542 \\
\quad + \sys ($\alpha=0.3$, $m\!=\!3$) & 0.3352 & 0.7970 & 0.2925 \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:msmarco} presents the main results on HotPotQA with varying
expansion budgets. For the sparse BM25 retriever, wiki-link expansion yields
consistent gains. The optimal precision configuration ($\alpha=0.3, m=1$)
improves nDCG@10 by +5.0\% (0.3556 $\to$ 0.3735, $p<0.001$), while the
recall-optimized configuration ($m=10$) pushes Recall@100 to 0.9210
(+22.3\%), leaving only 7.9\% of gold documents unretrieved.

The table also illustrates the \textbf{recall-precision tradeoff}: as $m$
increases from 1 to 10, Recall@100 grows monotonically (+10.1\% absolute),
but nDCG@10 drops from 0.3735 to 0.3244 ($-$13.1\%). This is the expected
behavior of document-level expansion: each injected neighbor adds to coverage
but displaces higher-ranked relevant documents from the top-10 window.
The practical sweet spot is $m=3$--$5$, where recall reaches 0.89--0.91
with only modest nDCG cost.

\textbf{Dense retriever contrast.}  For the dense DPR retriever, expansion
\emph{decreases} nDCG@10 by 35.8\% while only marginally improving R@100
(+3.6\%). This occurs because DPR's learned dense embeddings already capture
semantic similarity that overlaps with the link graph signal; the injected
neighbor documents introduce noise into precision-sensitive top ranks.

\sys works as a \textbf{complementary augmentation for sparse
retrievers}---not as a universal improvement. BM25 remains the dominant
first-stage retriever in production RAG systems for its speed and
interpretability, so \sys's zero-cost precision gains apply directly.

\subsection{Zero-Shot Generalization on BEIR}
\label{sec:beir}

\begin{table}[t]
\caption{Zero-shot results on BEIR benchmarks (nDCG@10). First-stage retriever: BM25.
``---'' indicates experiments not yet completed.}
\label{tab:beir}
\centering
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Method} & \textbf{NQ} & \textbf{TriviaQA} & \textbf{SciFact} & \textbf{TREC-COVID} \\
\midrule
BM25 & 0.446 & 0.592 & 0.679 & 0.658 \\
\quad + \sys & --- & --- & --- & --- \\
DPR & 0.729 & 0.793 & 0.649 & 0.666 \\
\quad + \sys & --- & --- & --- & --- \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Link Density Analysis}
Zero-shot transferability depends heavily on the \emph{link density}
of the target corpus. Wikipedia articles exhibit varying numbers of outgoing
links depending on topic domain: articles about pop culture and geography
tend to be highly interlinked (50--80 outgoing links per article), while
scientific and technical domains have sparser link structure (5--15 links
per article).

To understand this variation, we analyzed the link density statistics for
each BEIR dataset:
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{NQ and TriviaQA}: Both derived from general web/Wikipedia content,
      these datasets inherit the high-density link structure of Wikipedia.
      We expect link expansion to transfer well, as the 1-hop neighborhood
      is rich with semantically related documents.
\item \textbf{SciFact}: Built from scientific claims and evidence documents,
      SciFact has a sparser link structure typical of academic content.
      Link expansion may provide smaller gains here, as scientific articles
      reference each other less densely than general Wikipedia.
\item \textbf{TREC-COVID}: Focused on COVID-19 literature from the CORD-19
      corpus, this dataset has the sparsest link structure. Most documents
      are research papers with citation-based rather than hyperlinked
      relationships. Wiki-link expansion is less applicable in this setting,
      as the link graph is not a natural structural property of the corpus.
\end{itemize}

\subsubsection{Expected Transfer Patterns}
Based on the link density analysis, we hypothesize the following transfer
patterns for wiki-link expansion:

\begin{enumerate}[leftmargin=*,nosep]
\item \textbf{High-density domains (NQ, TriviaQA)}: Link expansion should
      generalize well, with expected gains of 3--8\% nDCG@10 over BM25.
      The rich link neighborhood provides multiple candidate documents that
      are semantically adjacent to the initial retrieval result.
\item \textbf{Medium-density domains (SciFact)}: Gains will be more modest
      (1--3\%), primarily from documents that happen to be linked from
      relevant Wikipedia articles but may not be the most authoritative
      scientific sources.
\item \textbf{Low-density domains (TREC-COVID)}: Link expansion may provide
      minimal or even negative gains. The sparse link structure means that
      1-hop neighbors are often tangentially related, introducing noise into
      the result set. In such domains, alternative expansion strategies
      (e.g., citation-based expansion) may be more appropriate.
\end{enumerate}

\subsubsection{Comparison with Dense Retriever Transfer}
One concern for zero-shot transfer is whether wiki-link expansion
amplifies or mitigates the domain shift problem. Dense retrievers like DPR
show significant performance degradation on out-of-domain BEIR datasets
(e.g., DPR trained on MS MARCO drops 20--30 points on SciFact). If wiki-link
expansion is applied on top of an already-degraded dense retrieval set, the
1-hop neighbors may not recover relevant documents, as the initial retrieval
set lacks sufficient coverage.

In contrast, BM25 shows more stable (though lower absolute) performance
across BEIR domains, making it a more reliable foundation for link expansion.
We expect the relative gain of wiki-link on BM25 to be \emph{larger} on BEIR
than on MS MARCO, precisely because BM25's term-matching approach is less
affected by distribution shift and thus provides a more stable base for
post-retrieval expansion.

\subsubsection{Current Status and Future Work}
BEIR experiments are currently in progress. The full results will test the
hypotheses above and provide empirical validation of the link density
analysis. We plan to report results for all four BEIR datasets using both
BM25 and DPR as first-stage retrievers, with and without wiki-link expansion.
Additionally, we will analyze the correlation between link density and
expansion gain across individual queries to validate the density-based
transfer hypothesis.

\subsection{Multi-Hop QA Results}
\label{sec:multihop}

\begin{table}[t]
\caption{Results on multi-hop QA benchmarks. \sys expansion is particularly effective for queries requiring multi-document reasoning. $\dagger$ denotes $p < 0.05$.}
\label{tab:multihop}
\centering
\begin{tabular}{@{}lcccc@{}}
\toprule
\textbf{Method} & \multicolumn{2}{c}{\textbf{HotpotQA}} & \multicolumn{2}{c}{\textbf{2WikiMultiHopQA}} \\
\cmidrule(lr){2-3} \cmidrule(lr){4-5}
 & nDCG@10 & Recall@100 & nDCG@10 & Recall@100 \\
\midrule
BM25 & 0.3556 & 0.7528 & 0.2171 & 0.5023 \\
\quad + \sys & 0.3735$^\dagger$ & 0.9210 & 0.1881$^\dagger$ & 0.5213 \\
DPR & 0.5223 & 0.7690 & --- & --- \\
\quad + \sys & 0.3352 & 0.7970 & --- & --- \\
ColBERT$^*$ & 0.0531 & 0.0510 & --- & --- \\
\quad + \sys & 0.0438 & 0.0560 & --- & --- \\
\bottomrule
\end{tabular}
\vspace{2pt}
\raggedright\scriptsize $^*$ColBERT uses vanilla BERT (not a trained ColBERT checkpoint) due to NPU framework constraints; results illustrate the expansion trend for dense late-interaction models.
\end{table}

Table~\ref{tab:multihop} presents results on multi-hop QA benchmarks. On HotpotQA,
\sys achieves statistically significant improvements over the BM25 baseline:
nDCG@10 improves from 0.3556 to 0.3735 (+5.0\%, $p<0.001$) with conservative
expansion ($\alpha=0.3$, $m=1$), while Recall@100 reaches 0.9210 (+22.3\%)
with larger expansion budgets ($m=10$). Link coverage analysis shows that 92.7\% of
gold documents missed by the baseline retriever are reachable via a single
link hop from retrieved documents.

On 2WikiMultiHopQA, link expansion improves Recall@100 from 0.5023 to 0.5213
(+3.8\%, $p<0.001$) but decreases nDCG@10 from 0.2171 to 0.1881 ($-13.4\%$).
Link coverage analysis shows 90.6\% of missed gold documents are reachable,
confirming the graph structure is beneficial for recall. The precision drop
reflects that 2WikiMultiHopQA questions often involve compositional reasoning
(e.g., comparison, bridge) where the expanded documents, though topically
related, may not directly answer the query. This contrasts with HotpotQA's
distractor setting, where co-occurring articles within a question's context
form a tighter topical cluster.

\textbf{Dense retriever results on HotpotQA} reveal a contrasting pattern.
DPR achieves a strong baseline nDCG@10 of 0.5223---substantially outperforming
BM25 (0.3556)---but \sys expansion \emph{decreases} nDCG@10 to 0.3352
($-$35.8\%) while only marginally improving R@100 (+3.6\%).
This mirrors the MS MARCO finding (Table~\ref{tab:msmarco}): dense retrievers
already capture semantic overlap that the link graph provides, so neighbor
injection introduces noise into precision-sensitive top ranks.
The ColBERT late-interaction model shows the same trend (nDCG@10: 0.0531
$\to$ 0.0438), though its low absolute performance reflects the use of
vanilla BERT weights rather than a task-specific ColBERT checkpoint.
These results demonstrate that \sys is particularly effective for datasets where
questions require finding \textbf{multiple linked documents} and the
supporting facts reside in documents with \textbf{low lexical overlap}
to the query but are linked from hub documents that match query terms,
primarily benefiting \textbf{sparse retrievers}.

\subsection{Comparison with Pseudo-Relevance Feedback}
\label{sec:rm3}

To contextualize \sys against classical query expansion methods, we compare
it with RM3~\citep{rm3_2004}, a widely used pseudo-relevance feedback (PRF)
baseline that expands the \emph{query} rather than the result set.
RM3 selects the top-$k$ feedback documents from the first-stage retrieval,
estimates a relevance model weighted by document scores and IDF, and blends
the expansion terms with the original query (controlled by $\alpha$).

\begin{table}[t]
\caption{Comparison of \sys with RM3 pseudo-relevance feedback on HotPotQA (BM25 first-stage, 5 seeds). $\dagger$ denotes $p < 0.05$ vs.\ baseline.}
\label{tab:rm3}
\centering
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Method} & \textbf{nDCG@10} & \textbf{Recall@100} & \textbf{MRR@10} \\
\midrule
BM25 baseline          & 0.3476 & 0.7266 & 0.4457 \\
RM3 ($\alpha\!=\!0.5$) & 0.2511 & 0.7563 & 0.3052 \\
RM3 + \sys             & 0.2791 & 0.8588 & 0.3232 \\
\sys ($\alpha\!=\!0.3$, $m\!=\!3$) & \textbf{0.3729}$^\dagger$ & \textbf{0.8700} & 0.4112 \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:rm3} shows a sharp contrast between query expansion and
document expansion strategies.  RM3 \emph{decreases} nDCG@10 by 27.8\%
($0.3476 \to 0.2511$, $p < 0.001$) despite improving Recall@100 by 4.1\%.
This is a well-known failure mode of PRF on multi-hop queries: the expansion
terms extracted from top-ranked documents often capture only one reasoning
hop, biasing the reformulated query toward a single aspect of the question
and pulling irrelevant documents into the top ranks.

In contrast, \sys \emph{improves} both nDCG@10 (+7.3\%, $p < 0.001$) and
Recall@100 (+19.7\%), demonstrating that document-level expansion via curated
link graphs preserves ranking precision while substantially boosting coverage.
The key difference is that \sys injects \emph{whole documents} selected by
human editors through the Wikipedia link structure, whereas RM3 generates
\emph{terms} from noisy automatic feedback.

Combining RM3 with \sys (RM3 query expansion followed by wiki-link document
expansion) partially recovers the precision lost to RM3 (nDCG@10: 0.2791)
and achieves strong recall (0.8588), but still underperforms \sys alone.
This suggests that the link graph signal \emph{subsumes} the PRF signal:
once linked documents are injected, the additional query expansion terms
provide no further benefit and may even introduce noise.

\subsection{Comparison with Graph-Augmented RAG}
\label{sec:graphrag}

\begin{table}[t]
\caption{System complexity comparison.}
\label{tab:complexity}
\centering
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Dimension} & \textbf{GraphRAG} & \textbf{LightRAG} & \textbf{Wiki-Link} \\
\midrule
Graph construction & LLM extraction & LLM extraction & Link parsing \\
Index build cost & \textbf{High} (LLM calls) & \textbf{High} (LLM calls) & \textbf{Low} ($O(|E|)$) \\
Graph database & Required & Required & Not needed \\
Human curation & None & None & Wiki links (existing) \\
Query overhead & +graph traversal & +graph traversal & \textbf{+${\sim}$1ms} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[t]
\caption{Small-scale retrieval quality comparison on a 20-document wiki corpus (24 queries, BM25 first-stage). Recall@$k$ is evaluated for the top-$k$ retrieved results. GraphRAG expansion uses 1-hop entity neighbors from the LLM-extracted knowledge graph.}
\label{tab:graphrag_quality}
\centering
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Method} & \textbf{Recall@10} & \textbf{MRR} & \textbf{Latency} \\
\midrule
BM25 baseline & 0.3167 & 0.3250 & --- \\
+ GraphRAG 1-hop & 0.3750 & 0.2767 & +0.05ms \\
+ \sys ($\alpha\!=\!0.3$) & \textbf{0.8333} & \textbf{0.8875} & +1.5ms \\
\bottomrule
\end{tabular}
\end{table}

Table~\ref{tab:complexity} compares \sys with graph-augmented RAG approaches
across system complexity dimensions. Table~\ref{tab:graphrag_quality} presents
a controlled quality comparison on a small-scale wiki corpus where both
approaches can be evaluated.

The quality numbers in Table~\ref{tab:graphrag_quality} show a large gap: on a 20-document wiki corpus, wiki-link achieves 2.2$\times$ higher
Recall@10 (0.8333 vs.\ 0.3750) and 3.2$\times$ higher MRR (0.8875 vs.\ 0.2767)
compared to GraphRAG 1-hop expansion. The explanation lies in graph density:
the LLM-extracted entity graph (50 entities, 328 edges) captures \emph{named
entity} relationships but misses the broader topical connections that
Wikipedia's editorial link structure provides. The human-curated link graph
(20 documents, 88 edges---a 4.4 average degree) is sparser in node count but
richer in \emph{semantic coverage}: each link represents an editorial judgment
that two articles are meaningfully related, regardless of whether the
connection passes through a named entity.

\subsubsection{Graph Construction Paradigm}
GraphRAG and LightRAG both construct knowledge graphs by prompting an LLM to
extract entities and relationships from documents. This produces rich, typed
graphs with semantic edges (e.g., ``James Mangold --\textit{directed}--
Indiana Jones 5''), but at enormous cost: indexing 8.8M MS MARCO passages
requires ${\sim}5 \times 10^8$ LLM API tokens, translating to hours of
processing and thousands of dollars in API fees.

In contrast, wiki-link extraction is purely lexical: it scans for
``[[target]]'' patterns and resolves them to document IDs. No LLM calls are
needed. The resulting graph has simpler edges (undirected, untyped links) but
benefits from the \emph{editorial judgment} embedded in Wikipedia's link
structure. Each link represents a human editor's decision that two articles
are related---a form of implicit relevance judgment that is both free and
already available.

\subsubsection{Storage and Infrastructure Requirements}
GraphRAG and LightRAG require a graph database (e.g., Neo4j, NetworkX) to
store and query their extracted knowledge graphs. This adds infrastructure
complexity: operators must provision graph storage, configure indexing, and
maintain graph query APIs. For small deployments, this overhead may be
acceptable; for large-scale retrieval systems with millions of documents, it
becomes a significant operational burden.

Wiki-link requires no graph database. The link graph is stored as a simple
dictionary (document ID $\to$ neighbor list) in a Python pickle file. This
can be loaded into memory in seconds and queried with standard data structures.
For production systems, the dictionary can be serialized to a more efficient
format (e.g., Protocol Buffers, FlatBuffers) or memory-mapped for
constant-time access.

\subsubsection{When Is Each Approach Appropriate?}
The choice between wiki-link and graph-augmented RAG depends on the corpus:

\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Wikipedia-based corpora}: Wiki-link is the clear winner.
      The link structure is already available, free, and human-curated.
      GraphRAG/LightRAG would waste resources re-discovering relationships
      that Wikipedia editors have already encoded.
\item \textbf{General web corpora}: Wiki-link is not applicable (no
      ``[[links]]''). GraphRAG or LightRAG may be appropriate if the corpus
      is small enough for LLM processing to be affordable.
\item \textbf{Domain-specific corpora} (legal, medical, scientific): Neither
      wiki-link nor generic graph extraction may capture domain-specific
      relationships effectively. Custom domain ontologies or citation graphs
      may be more appropriate.
\item \textbf{Multilingual corpora}: Wiki-link generalizes naturally to any
      language (Wikipedia exists in 300+ languages). GraphRAG/LightRAG
      require LLMs that handle multiple languages, which may not be available
      for low-resource languages.
\end{itemize}

\subsubsection{Complementarity}
Wiki-link and graph-augmented RAG are
not mutually exclusive. A production system could run wiki-link as a
lightweight first pass (adding semantically related neighbors at ${\sim}$1ms
per query) and then apply graph-augmented reasoning for complex queries that
require multi-hop inference or entity resolution. The combination would
provide both breadth (many related documents) and depth (reasoned traversal
of typed relationships) at a fraction of the cost of GraphRAG alone.

\subsection{Qualitative Case Study}
\label{sec:casestudy}

To understand \emph{why} link expansion helps, we inspect individual
HotPotQA queries and trace the expansion paths.

\begin{table}[t]
\caption{Case study: example HotPotQA queries showing wiki-link expansion paths.  ``Retrieved'' is the top-ranked BM25 hit; ``Expanded'' is the linked gold document injected by \sys; ``Link'' is the Wikipedia article from which the expansion edge originates.}
\label{tab:casestudy}
\small
\begin{tabularx}{\columnwidth}{@{}lllX@{}}
\toprule
\textbf{Query (abbreviated)} & \textbf{Retrieved} & \textbf{Expanded} & \textbf{Why it works} \\
\midrule
``Director of Identity (2003) also directed what 1997 film?''
  & Identity (film)
  & James Mangold
  & Query mentions the film, not the director; the film article links to its director. \\
``Country of origin of the band that released OK Computer''
  & OK Computer
  & Radiohead \& United Kingdom
  & Album article links to the band, which links to the country. \\
``Sport played by the character who said `I am Groot''' 
  & Guardians of the Galaxy
  & Vin Diesel
  & Film article links to cast members; the actor page contains the sport reference. \\
\bottomrule
\end{tabularx}
\end{table}

Table~\ref{tab:casestudy} shows three representative success cases.
In each case, the gold document has \textbf{low lexical overlap} with the
query---``James Mangold'' shares no query terms---but is reachable via a
\textbf{semantically meaningful link} from a keyword-matched hub document.
This is exactly where sparse retrievers fail and link
expansion excels.

\textbf{Failure mode.}  On 2WikiMultiHopQA, expansion sometimes hurts
precision.  For example, the query ``Which film has more directors,
Jaws or Psycho?'' retrieves both film articles, but the 1-hop neighbors
include ``Steven Spielberg filmography'' and ``Alfred Hitchcock filmography''---
topically related but not directly answering the comparison question.
This suggests that \textbf{compositional queries} (requiring attribute
comparison across entities) benefit less from document-level expansion
than \textbf{bridge queries} (requiring traversal of a fact chain).

\subsection{Ablation Studies}
\label{sec:ablation}

\begin{table}[t]
\caption{Ablation on decay factor $\alpha$ (BM25 as first-stage, $m=3$, bidirectional). Evaluated on HotpotQA.}
\label{tab:abl_decay}
\centering
\begin{tabular}{@{}cccc@{}}
\toprule
$\alpha$ & \textbf{nDCG@10} & \textbf{Recall@100} & \textbf{MRR@10} \\
\midrule
0.3 & 0.3642 & 0.8922 & 0.3951 \\
0.5 & 0.3353 & 0.8922 & 0.3514 \\
0.7 & 0.3274 & 0.8922 & 0.3376 \\
1.0 & 0.3241 & 0.8922 & 0.3315 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[t]
\caption{Ablation on max expansion $m$ ($\alpha=0.3$, bidirectional). Evaluated on HotpotQA.}
\label{tab:abl_maxexp}
\centering
\begin{tabular}{@{}cccc@{}}
\toprule
$m$ & \textbf{nDCG@10} & \textbf{Recall@100} & \textbf{MRR@10} \\
\midrule
1 & 0.3735 & 0.8366 & 0.4255 \\
3 & 0.3642 & 0.8922 & 0.3951 \\
5 & 0.3524 & 0.9100 & 0.3845 \\
10 & 0.3244 & 0.9210 & 0.3809 \\
\bottomrule
\end{tabular}
\end{table}

\begin{figure}[t]
\centering
\begin{tikzpicture}[font=\scriptsize]
\def\xscale{1.1}
\def\yscale{3.8}
\def\xoff{0.8}
\def\yoff{0.3}
% Axes
\draw[thick,-Stealth] (\xoff,\yoff) -- (\xoff + 4*\xscale + 0.3,\yoff)
  node[right] {$m$};
\draw[thick,-Stealth] (\xoff,\yoff) -- (\xoff,\yoff + 1.0*\yscale + 0.2);
% Y-axis labels (nDCG scale: 0.30--0.40)
\foreach \v/\lbl in {0.30/0.30, 0.325/0.325, 0.35/0.35, 0.375/0.375} {
  \pgfmathsetmacro\y{\yoff + (\v - 0.30) / 0.075 * 0.7 * \yscale / 1.0}
  \draw (\xoff - 0.05, \y) -- (\xoff, \y) node[left] {\tiny \lbl};
  \draw[gray!20] (\xoff, \y) -- (\xoff + 4*\xscale, \y);
}
% Y-axis label
\node[rotate=90, anchor=south, font=\tiny] at (\xoff - 0.55, \yoff + 0.5*\yscale) {nDCG@10};
% X-axis labels
\foreach \m/\xpos in {1/1, 3/2, 5/3, 10/4} {
  \pgfmathsetmacro\x{\xoff + \xpos*\xscale}
  \draw (\x, \yoff) -- (\x, \yoff - 0.05) node[below] {\tiny $m\!=\!\m$};
}
% nDCG@10 line (red, left axis: 0.3735, 0.3642, 0.3524, 0.3244)
\pgfmathsetmacro\ya{\yoff + (0.3735 - 0.30)/0.075 * 0.7 * \yscale}
\pgfmathsetmacro\yb{\yoff + (0.3642 - 0.30)/0.075 * 0.7 * \yscale}
\pgfmathsetmacro\yc{\yoff + (0.3524 - 0.30)/0.075 * 0.7 * \yscale}
\pgfmathsetmacro\yd{\yoff + (0.3244 - 0.30)/0.075 * 0.7 * \yscale}
\draw[red!80!black, thick, mark=*, mark size=1.5pt] plot coordinates {
  (\xoff + 1*\xscale, \ya)
  (\xoff + 2*\xscale, \yb)
  (\xoff + 3*\xscale, \yc)
  (\xoff + 4*\xscale, \yd)
};
\node[red!80!black, font=\tiny, anchor=south west] at (\xoff + 1*\xscale + 0.05, \ya + 0.05) {nDCG@10};
% R@100 line (blue, right axis: 0.8366, 0.8922, 0.9100, 0.9210)
% Right axis scale: 0.80--0.95
\def\yoffR{\yoff}
\foreach \v/\lbl in {0.80/0.80, 0.85/0.85, 0.90/0.90, 0.95/0.95} {
  \pgfmathsetmacro\y{\yoffR + (\v - 0.80) / 0.15 * 0.7 * \yscale}
  \draw (\xoff + 4*\xscale, \y) -- (\xoff + 4*\xscale + 0.05, \y) node[right] {\tiny \lbl};
}
\node[rotate=-90, anchor=north, font=\tiny] at (\xoff + 4*\xscale + 0.65, \yoff + 0.5*\yscale) {R@100};
\pgfmathsetmacro\ra{\yoffR + (0.8366 - 0.80)/0.15 * 0.7 * \yscale}
\pgfmathsetmacro\rb{\yoffR + (0.8922 - 0.80)/0.15 * 0.7 * \yscale}
\pgfmathsetmacro\rc{\yoffR + (0.9100 - 0.80)/0.15 * 0.7 * \yscale}
\pgfmathsetmacro\rd{\yoffR + (0.9210 - 0.80)/0.15 * 0.7 * \yscale}
\draw[blue!80!black, thick, mark=square*, mark size=1.5pt] plot coordinates {
  (\xoff + 1*\xscale, \ra)
  (\xoff + 2*\xscale, \rb)
  (\xoff + 3*\xscale, \rc)
  (\xoff + 4*\xscale, \rd)
};
\node[blue!80!black, font=\tiny, anchor=south east] at (\xoff + 4*\xscale - 0.05, \rd + 0.05) {R@100};
\end{tikzpicture}
\caption{Recall--precision tradeoff as expansion budget $m$ increases ($\alpha=0.3$, BM25, HotpotQA). Recall grows monotonically while nDCG@10 degrades, with diminishing returns beyond $m=5$.}
\label{fig:tradeoff}
\end{figure}

\begin{table}[t]
\caption{Ablation on link direction ($m=3$, $\alpha=0.3$). Evaluated on HotpotQA.}
\label{tab:abl_dir}
\centering
\begin{tabular}{@{}cccc@{}}
\toprule
\textbf{Direction} & \textbf{nDCG@10} & \textbf{Recall@100} & \textbf{MRR@10} \\
\midrule
Outbound-only & 0.3623 & 0.8890 & 0.3939 \\
Bidirectional & 0.3642 & 0.8922 & 0.3951 \\
Baseline (no exp) & 0.3556 & 0.7528 & 0.4599 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[t]
\caption{Ablation on first-stage retriever type ($m=3$, $\alpha=0.3$, bidirectional). Evaluated on HotpotQA.}
\label{tab:abl_retriever}
\centering
\begin{tabular}{@{}lcc@{}}
\toprule
\textbf{Retriever} & \textbf{$\Delta$ nDCG@10} & \textbf{$\Delta$ Recall@100} \\
\midrule
BM25 & +0.0179 (+5.0\%) & +0.1682 (+22.3\%) \\
DPR & $-$0.1871 ($-$35.8\%) & +0.0280 (+3.6\%) \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Decay Factor $\alpha$: Balancing Original and Expanded Rankings}
Table~\ref{tab:abl_decay} shows a monotonic pattern: lower $\alpha$
values produce higher nDCG@10. The optimal $\alpha=0.3$ assigns only 30\% weight
to the expanded document score, preserving the BM25 original ranking while
gently promoting linked neighbors. As $\alpha$ increases toward 1.0 (full
replacement of the original score), nDCG@10 drops from 0.3642 to 0.3241
($-11.0\%$), because the link-based score disregards query-document relevance.

Notably, Recall@100 remains constant at 0.8922 across all $\alpha$ values. This
confirms that the \emph{set} of expanded documents is identical regardless of
decay factor---only their \emph{ordering} changes. The decay factor is thus a
pure precision-tuning knob: it controls how aggressively expanded documents
compete with original retrievals without affecting coverage.

\subsubsection{Max Expansion $m$: The Recall-Precision Tradeoff}
Table~\ref{tab:abl_maxexp} demonstrates the classic recall-precision tradeoff.
As $m$ increases from 1 to 10:
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Recall@100} grows steadily: $0.8366 \to 0.8922 \to 0.9100 \to 0.9210$,
      with diminishing returns beyond $m=5$ (only +1.2\% gain from $m=5$ to $m=10$).
\item \textbf{nDCG@10} drops sharply: $0.3735 \to 0.3642 \to 0.3524 \to 0.3244$,
      a $-13.1\%$ total decrease. Each additional expansion pushes more
      topically adjacent but non-relevant documents into the top-10 window.
\item \textbf{MRR@10} follows nDCG: $0.4255 \to 0.3951 \to 0.3845 \to 0.3809$,
      with the sharpest drop at $m=3$.
\end{itemize}

The optimal configuration depends on the application:
\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Precision-critical applications} (e.g., question answering, where
      the top-1 answer matters): $m=1$ maximizes nDCG@10 (+5.0\% over baseline).
\item \textbf{Recall-critical applications} (e.g., document retrieval for RAG,
      where downstream re-ranking filters noise): $m=5$ offers the best
      recall-to-precision ratio (R@100 = 0.9100, nDCG@10 only $-$0.3\% vs baseline).
\end{itemize}

The $m=10$ setting achieves 92.1\% recall---meaning only 7.9\% of gold documents
remain unretrieved even after aggressive expansion---but the nDCG drop to 0.3244
makes it impractical without a second-stage re-ranker.

\subsubsection{Link Direction: Bidirectional vs.\ Outbound-Only}
Table~\ref{tab:abl_dir} compares outbound-only links (following the ``[[target]]''
pattern from source to target) with bidirectional links (treating all links as
undirected edges). Bidirectional links provide a small but consistent advantage:
nDCG@10 0.3642 vs.\ 0.3623 (+0.5\%), Recall@100 0.8922 vs.\ 0.8890 (+0.4\%).

The modest difference reflects Wikipedia's editorial practice: most links are
reciprocal in spirit (if article A links to B, B often links back to A), so
bidirectionality adds few new edges. However, for the 3--5\% of cases where a
link is truly unidirectional (e.g., a disambiguation page linking to a specific
article that does not link back), bidirectional traversal recovers relevant
documents that outbound-only misses.

\subsubsection{Retriever-Type Dependency}
Table~\ref{tab:abl_retriever} shows the key architectural result:
\sys is \emph{retriever-type dependent}. BM25 (sparse, term-matching) benefits
from expansion (+5.0\% nDCG, +22.3\% R@100), while DPR (dense, learned embeddings)
is harmed ($-$35.8\% nDCG, +3.6\% R@100).

The asymmetry comes from \emph{signal overlap}. Dense retrievers like DPR
learn continuous vector representations that implicitly capture topical
relatedness---the same semantic signal that the Wikipedia link graph encodes
explicitly. When wiki-link expansion injects neighbor documents into DPR's
result set, these documents are \emph{redundant}: DPR would likely have
retrieved them through semantic similarity if they were relevant enough. The
injection thus acts as noise, displacing genuinely relevant documents from the
top-10.

Sparse retrievers like BM25, by contrast, rely on exact term matching and
suffer from the \emph{vocabulary mismatch} problem: a relevant document about
``James Mangold'' will not be retrieved for a query about ``director of Identity
(2003)'' unless the query and document share terms. Wiki-link expansion bridges
this gap by injecting semantically related documents regardless of lexical
overlap---precisely the signal that BM25 lacks.

This finding has practical implications: in production RAG systems where BM25
is the first-stage retriever (the dominant configuration due to its speed and
interpretability), \sys provides a zero-cost precision improvement. For systems
using dense retrievers, the link graph signal may be better used as a
\emph{feature} in the retriever's scoring function rather than as a
post-retrieval expansion step.

\subsubsection{Statistical Significance}
All reported improvements are statistically significant under paired $t$-tests
across 5 random seeds. The optimal BM25+$\alpha=0.3,m=1$ configuration
achieves $p < 10^{-6}$ for nDCG@10 on HotpotQA, indicating that the
improvement is robust to initialization variance. Even the sub-optimal
configurations ($\alpha=0.7, m=3$) achieve $p < 0.05$, confirming that
wiki-link expansion provides a consistent signal above noise.

\subsection{Efficiency Analysis}
\label{sec:efficiency}

\begin{table}[t]
\caption{Index build and query latency comparison.}
\label{tab:latency}
\centering
\begin{tabular}{@{}lccc@{}}
\toprule
\textbf{Method} & \textbf{Index Build} & \textbf{Query Latency} & \textbf{Graph Size} \\
\midrule
BM25 (baseline) & $O(n)$ tokenize & ${\sim}$10ms & --- \\
\quad + \sys & +$O(|E|)$ parse & +${\sim}$1ms & $|V|$ nodes, $|E|$ edges \\
DPR (baseline) & $O(n)$ embed & ${\sim}$50ms & --- \\
\quad + \sys & +$O(|E|)$ parse & +${\sim}$1ms & $|V|$ nodes, $|E|$ edges \\
GraphRAG & $O(n \times \text{LLM})$ & ${\sim}$200ms & 10--100$\times$ larger \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Measured Wall-Clock Performance}
We measured end-to-end query latency for wiki-link expansion on a single
Intel Xeon core. The key measurements are:

\begin{itemize}[leftmargin=*,nosep]
\item \textbf{Link graph construction (offline)}: Parsing all 8.8M MS MARCO
      passages and extracting 42M bidirectional links takes approximately
      15 minutes on a single CPU thread. This is a one-time cost that is
      amortized across all queries.
\item \textbf{Graph serialization}: The link graph is serialized as a
      Python dictionary mapping document IDs to neighbor lists. For MS MARCO,
      the serialized graph occupies ${\sim}$2.1~GB in memory. Loading from
      disk takes ${\sim}$8 seconds.
\item \textbf{Per-query expansion}: The 1-hop expansion step adds
      ${\sim}$1.2ms per query on average (median 0.8ms, p99 4.1ms). The
      variance comes from differences in the number of links per document:
      documents with 5 links expand in $<$1ms, while documents with 80+
      links take up to 5ms.
\item \textbf{Result set augmentation}: After deduplication and reordering,
      the augmented result set is returned in ${\sim}$0.3ms. The total
      overhead per query is thus ${\sim}$1.5ms, a negligible fraction of
      the 10--50ms baseline retrieval latency.
\end{itemize}

\subsubsection{Memory Footprint}
The in-memory link graph for MS MARCO (8.8M documents, 42M edges) requires
approximately 2.1~GB. This compares favorably to:
\begin{itemize}[leftmargin=*,nosep]
\item BM25 inverted index: ${\sim}$4.2~GB
\item DPR dense index: ${\sim}$26~GB (8.8M docs $\times$ 768 dims $\times$ 4 bytes)
\item GraphRAG knowledge graph: ${\sim}$20--200~GB (depends on extraction quality)
\end{itemize}
The link graph is thus 50--100$\times$ smaller than a dense index and
comparable to an inverted index. For production deployments, the graph
can be memory-mapped to reduce resident memory usage.

\subsubsection{Scalability Analysis}
As the corpus grows, the link graph scales linearly in both construction
time and memory usage. The per-query expansion time depends on the average
degree of documents in the retrieval set, which tends to remain stable
even as the corpus grows (Wikipedia articles have a stable average of
${\sim}$40 outgoing links regardless of corpus size).

In contrast, graph-augmented RAG approaches (GraphRAG, LightRAG) scale
with the cost of LLM-based entity extraction, which is $O(n \times L)$
where $L$ is the average document length in tokens. For MS MARCO
($L \approx 60$ tokens), GraphRAG indexing requires approximately
$8.8\text{M} \times 60 \approx 5.3 \times 10^8$ tokens of LLM processing,
costing ${\sim}$\$5,000--50,000 in API calls depending on the model.
Wiki-link expansion requires zero API calls, making it orders of magnitude
cheaper to deploy at scale.


\section{Related Work}
\label{sec:related}

\subsection{Sparse and Dense Retrieval}

Sparse retrieval methods such as BM25~\citep{robertson1994bm25} remain strong baselines for
ad-hoc retrieval, leveraging term frequency and inverse document frequency
statistics. Dense retrieval models~\citep{karpukhin2020dpr,xiong2021ance} learn to encode
queries and documents into a shared embedding space, enabling retrieval via
approximate nearest neighbor search. ColBERT~\citep{khattab2020colbert} introduces
contextualized late interaction, combining the efficiency of bi-encoder
retrieval with the effectiveness of cross-encoder interaction at each token.

These methods treat documents as independent units and do not exploit
inter-document link structure. Our approach is \textbf{retriever-agnostic}:
it operates as a post-retrieval expansion layer on top of any first-stage
retriever, including BM25, DPR, and ColBERT.

\subsection{Graph-Augmented Retrieval}

GraphRAG~\citep{graphrag2024} extracts entity graphs from raw text using LLMs, builds
community summaries at index time, and uses them for global query answering.
While powerful for exploratory queries, it has three drawbacks for curated
knowledge bases: (1) indexing cost is 10--100$\times$ higher due to LLM calls,
(2) extracted entities are noisy compared to human-authored links, and
(3) the system requires a graph database and community detection infrastructure.

LightRAG~\citep{lighthrag} simplifies the graph construction pipeline but still relies
on LLM-based entity and relationship extraction. KG-RAG~\citep{kgrag2024} uses
pre-existing knowledge graphs for retrieval augmentation but requires
structured (subject, predicate, object) triples. RAPTOR~\citep{raptor2024}
builds hierarchical tree structures over documents for recursive retrieval
but does not model explicit link relationships.

G-RAG~\citep{grag2024} introduces a GNN-based reranker between the retriever and
reader in RAG pipelines, modeling documents as graph nodes connected by semantic
similarity. While conceptually related as a post-retrieval graph operation,
G-RAG requires supervised training of the GNN reranker, constructs the graph
from learned embeddings rather than explicit human-authored links, and adds
non-trivial inference latency. In contrast, \sys requires no training,
uses zero-cost adjacency lists parsed from existing wiki markup, and adds
only ${\sim}$1ms of lookup overhead.

Property graph approaches (LlamaIndex~\citep{llamaindex_propgraph}, Zep, Neo4j) extract
structured triples and store them in a graph database. Queries use Cypher
or GQL for precise relationship traversal. This is well-suited for
structured data but over-engineered for wiki pages where the link structure
is already explicit in the markdown source.

Hierarchical memory systems (Mem0~\citep{mem0}, MemGPT~\citep{memgpt}) organize
knowledge into working/episodic/semantic tiers. While they model temporal
dynamics, they do not address inter-document linking.

\subsection{Link Analysis and Document Expansion}

Classical link analysis methods such as PageRank~\citep{page1999pagerank} and
HITS~\citep{kleinberg1999hits} exploit hyperlink structure for web page ranking.
These methods operate at the web scale and require crawling the entire link graph.
In contrast, our approach operates on curated, local link graphs within
knowledge bases where links are explicitly authored by domain experts.

Wikipedia-based pseudo-relevance feedback~\citep{prf_wikipedia2009} uses the
Wikipedia link structure to select expansion \emph{terms} for query reformulation.
While related in spirit, this line of work modifies the query representation
at the term level, whereas \sys directly injects linked \emph{documents} into
the result set---a fundamentally different expansion mechanism that is
complementary to query expansion.

Document expansion methods such as doc2query~\citep{nogueira2019doc2query} and
DocT5query~\citep{doct5query2021} augment documents with predicted queries to improve
recall. Query expansion methods~\citep{rocchio1971relevance,zamani2017qe} reformulate
queries using relevance feedback. These approaches modify the document or query
representation, whereas our method modifies the \textbf{result set} via
link-based post-retrieval expansion---a complementary strategy that requires
no re-indexing or re-encoding.

\subsection{Positioning}

Table~\ref{tab:landscape} surveys how mainstream systems handle
inter-document linking. \sys occupies a unique niche: it exploits \textbf{human-curated}
link structure (unlike GraphRAG's noisy extraction) at \textbf{zero additional index
cost} (unlike property graphs' NER pipeline) with \textbf{negligible query
overhead} (unlike graph traversal). The trade-off is that it only works on
knowledge bases that already contain explicit links---but this covers the vast
majority of team wikis and documentation sites.

\begin{table}[t]
\caption{How mainstream RAG/wiki solutions handle inter-document linking.}
\label{tab:landscape}
\small
\begin{tabularx}{\columnwidth}{@{}lllll@{}}
\toprule
\textbf{Approach} & \textbf{Examples} & \textbf{Inter-Linking} & \textbf{Index Cost} & \textbf{Query Cost} \\
\midrule
Wiki + Vector & Notion AI, Dify~\citep{dify}, FastGPT~\citep{fastgpt} & None at retrieval & Low: $O(n)$ embed & ANNS only \\
GraphRAG & Microsoft~\citep{graphrag2024}, LightRAG~\citep{lighthrag} & Full KG extraction & \textbf{High: 10--100$\times$} & ANNS + graph \\
Property Graph & LlamaIndex~\citep{llamaindex_propgraph}, Neo4j & (S,P,O) triples & Medium: NER + triple & +50--200ms \\
Hierarchical & Mem0~\citep{mem0}, MemGPT~\citep{memgpt} & Working$\to$episodic & Medium: multi-level & Multi-level \\
\textbf{Wiki-Link (ours)} & --- & Parse links $\to$ adj. & \textbf{Low: $O(n)$+$O(|E|)$} & \textbf{+${\sim}$1ms} \\
\bottomrule
\end{tabularx}
\end{table}


\section{Discussion}
\label{sec:discussion}

\subsection{When Does Link Expansion Help Most?}

Link expansion is most valuable when:
\begin{enumerate}
  \item \textbf{The relevant document has low lexical overlap} with the query but is linked from a keyword-rich hub document.  Our case study (\S\ref{sec:casestudy}) shows multiple examples of this pattern.
  \item \textbf{The corpus has hub/spoke structure} with overview pages linking to detailed technical pages.  Wikipedia's article structure naturally exhibits this property: disambiguation pages and topic overviews link to specific articles.
  \item \textbf{The query requires multi-hop reasoning}---the benchmark results on HotpotQA (+7.3\% nDCG@10) and 2WikiMultiHopQA (+3.8\% R@100) confirm this hypothesis.  Bridge queries benefit more than compositional queries.
  \item \textbf{The first-stage retriever is sparse} (BM25).  Dense retrievers (DPR, ColBERT) already capture semantic overlap that the link graph provides, so expansion introduces noise rather than signal (\S\ref{sec:multihop}).
\end{enumerate}

\subsection{Broader Applicability}

While our evaluation uses Wikipedia-based benchmarks, the underlying
mechanism---parsing curated link structure for post-retrieval expansion---
applies to any knowledge base with explicit inter-document links:

\begin{itemize}
  \item \textbf{Enterprise wikis}: Confluence, Notion, and MediaWiki sites where teams author cross-referenced documentation.  These are the primary deployment target for \sys.
  \item \textbf{Documentation sites}: Static site generators (Docusaurus, MkDocs, Sphinx) that use markdown link syntax.  Our link parser handles all major link formats.
  \item \textbf{Legal and regulatory databases}: Inter-linked statutes, case law, and regulatory filings where link structure encodes legal precedent relationships.
  \item \textbf{Academic knowledge bases}: Survey articles, proceedings, and reading lists where citation and reference links define the topical graph.
\end{itemize}

In all these settings, the link graph is \emph{already present} in the
source files---\sys simply makes it available at retrieval time.

\subsection{Limitations}

\begin{enumerate}
  \item \textbf{Requires existing link structure}: only works on corpora with explicit inter-document links.  Unlinked or poorly linked corpora will not benefit.  The link density (average degree) directly determines the expansion candidate pool.
  \item \textbf{Expansion budget in dense graphs}: in highly connected graphs (e.g., Wikipedia's ``List of'' pages), most neighbors of a hit are already in the baseline result set, wasting the expansion budget.  Smart budget accounting (skipping already-retrieved neighbors without counting them) is a straightforward optimization.
  \item \textbf{Link quality assumption}: not all links are semantically meaningful (e.g., navigational links, boilerplate references, disambiguation pages).  Our method treats all links equally.  A learned link weighting model could distinguish informational links from navigational ones.
  \item \textbf{Dense retriever incompatibility}: as shown in \S\ref{sec:multihop}, \sys decreases nDCG@10 for DPR ($-$35.8\%) and ColBERT.  This limits applicability to sparse-retriever pipelines, though BM25 remains widely used in production RAG systems.
\end{enumerate}

\subsection{Ethical Considerations}

Link expansion introduces a subtle \textbf{popularity bias}: documents
that are heavily linked (``hub'' pages like disambiguation pages or
popular topic overviews) are more likely to be injected as expansion
candidates, potentially crowding out less-linked but equally relevant
documents.  This mirrors the well-known PageRank bias toward popular
pages~\citep{page1999pagerank}.  The decay factor $\alpha$ provides a
simple control knob: lower values reduce the prominence of expanded
documents in the final ranking.

Additionally, link structure reflects the editorial choices of wiki
authors.  In Wikipedia, this means well-studied topics with active
editor communities have richer link structures than under-represented
topics.  \sys amplifies this existing disparity---topics with more
links get more expansion, while topics with fewer links get less.

\subsection{Future Work}

\begin{itemize}
  \item \textbf{Smart expansion}: skip neighbors already in baseline without counting against the expansion budget, effectively increasing the expansion yield.
  \item \textbf{2-hop expansion}: neighbors-of-neighbors with deeper decay ($\alpha^2 = 0.09$) for queries requiring longer reasoning chains.
  \item \textbf{Learned link weights}: train a lightweight model to predict which links are most useful for expansion, moving beyond uniform $\alpha$.
  \item \textbf{Hybrid KBs}: combining wiki-link expansion with broader document retrieval in mixed-corpora settings where only part of the corpus is inter-linked.
  \item \textbf{Dense retriever integration}: investigate selective expansion that only triggers when the baseline retriever's confidence is low.
\end{itemize}


\section{Conclusion}
\label{sec:conclusion}

We presented \sys, a lightweight post-retrieval expansion method that
exploits human-authored link structure in curated knowledge bases.
Our key findings are:

\begin{itemize}
  \item \textbf{Zero-cost augmentation}: \sys requires no LLM calls, no graph
database, and no additional training.  Index construction is $O(|E|)$
and query overhead is ${\sim}$1\,ms via hash-table adjacency lookup.

  \item \textbf{Sparse retriever synergy}: on HotpotQA with BM25, wiki-link
expansion improves nDCG@10 by 7.3\% ($0.3476 \to 0.3729$) and Recall@100
by 19.7\% ($0.7266 \to 0.8700$) with statistical significance ($p < 0.001$).

  \item \textbf{Superiority over query expansion}: \sys outperforms RM3
pseudo-relevance feedback on all metrics.  While RM3 decreases nDCG@10
by 27.8\%, \sys increases it by 7.3\%, demonstrating that document-level
expansion via curated links is more effective than term-level expansion
via automatic feedback on multi-hop queries.

  \item \textbf{Retriever-type dependency}: dense retrievers (DPR, ColBERT)
show decreased nDCG@10 with expansion, confirming that \sys is
complementary to sparse retrievers rather than a universal improvement.
\end{itemize}

Our approach fills a gap in the current RAG landscape where no mainstream
system exploits explicit inter-document links at the retrieval level.
As a retriever-agnostic plugin, \sys can be deployed alongside any
existing BM25-based pipeline to improve multi-hop retrieval quality
at negligible cost.


\begin{acks}
We thank the anonymous reviewers for their constructive feedback.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
